Should I AirBNB My Property?

### 2017-01-05 abbReturns_Writeup.Rmd
Fixes to Data prep charts

```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}

@@

  abb.types <- ggplot(abb.data, aes(x=type)) + 
    geom_bar(color=str.col, fill=str.col) +
    xlab('') + 
    ggtitle('\n      Short Term Rentals\n')  +
    ylab('# of Properties\n')

@@

  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
    geom_bar(color=ltr.col, fill=ltr.col) +
    xlab('') + 
    ggtitle('\n      Long Term Rentals\n')  +
    ylab('# of Properties\n')

@@

```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}

@@

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}

@@

  ggplot(abb.data, aes(x=listing.type)) + 
    geom_bar(color=abb.col[1], fill=abb.col[1]) +
    xlab('') + 
    ggtitle('\n                           Short Term Rentals by Listing Type\n')  +
    ylab('# of Properties\n')

@@

```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}

@@

   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Long Term Rentals')

@@

  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:10, breaks=0:10)+
    xlab('\nBedrooms\n') +
    ylab('') +
    ggtitle('Bedrooms in Short Term Rentals')

@@

```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}

@@

  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Long Term Rentals')

@@

  stbath <- ggplot(abb.data, aes(x=baths)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') + 
    ggtitle('Bathrooms in Short Term ltrals')

@@

```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5}

@@

  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggtitle('Long Term Rentals') + 
    facet_wrap(~type)

@@

  stb <- ggplot(abb.data, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) + 
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type)

@@

  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
    geom_density(fill=ltr.col, alpha=.8) +
    ylab('') +
    xlab('Weekly Rental') + 
    ggtitle('Long Term Rentals') + 
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

  # Nightly Rate plot
  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
    geom_density(fill=str.col, alpha=.8) + 
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

@@

```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

@@

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=g.cols, labels=c('Inner      ',
                                              'Middle      ',
                                              'Outer')) +
    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray40') +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    ggtitle("Melbourne Suburb Classifications")

@@

```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=6}

@@

  abb.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('AirBNB Location\nBy Submarket')

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray50') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank()) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long Term Rental Location\nBy Submarket')

@@

```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}

@@

  abbtype.map <- ggplot() +
    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('AirBNB Property Type\nBy Submarket')

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('Long Term Property Type\nBy Submarket')

@@

```{r loctype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.width=9}

  ggMultiPlots(abbtype.map, ltrtype.map, cols=2)

>>>>

```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type'}

@@

  abb.types <- ggplot(abb.data, aes(x=type)) + 
    geom_bar(color=str.col, fill=str.col) +
    xlab('') + 
    ylab('# of Properties\n') +
    labs(title = "Short Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.types <- ggplot(ltr.data, aes(x=type)) + 
    geom_bar(color=ltr.col, fill=ltr.col) +
    xlab('') + 
    ylab('# of Properties\n') +
    labs(title = "Long Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap='Listing Type of Short Term Rentals'}

@@

  ggplot(abb.data, aes(x=listing.type)) + 
    geom_bar(color=abb.col[1], fill=abb.col[1]) +
    xlab('') + 
    ylab('# of Properties\n') +
    labs(title = "Short Term Rentals by Listing Type\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bedrooms by Tenure & Property Type'}

@@

   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bedrooms in Long Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  abbbed <- ggplot(abb.data, aes(x=bedrooms)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:10, breaks=0:10)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bedrooms in Short Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bathrooms by Tenure & Property Type'}

@@

  ltbath <- ggplot(ltr.data, aes(x=baths)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bathrooms in Long Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(abb.data, aes(x=baths)) + 
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bathrooms in Short Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Bed/Bath Combo by Tenure & Property Type'}

@@

  ltb <- ggplot(ltr.data, aes(x=bedbath)) + 
    geom_bar(fill=ltr.col, color=ltr.col) +
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bed/Bath Combo in Long Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
    facet_wrap(~type)

@@

  stb <- ggplot(abb.data, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) + 
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bed/Bath Combo in Short Term Rentals\n") + 
    theme(plot.title = element_text(hjust = 0.5)) + 
    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
    facet_wrap(~type)

@@

  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) + 
    geom_density(fill=ltr.col, alpha=.8) +
    ylab('Frequency') +
    xlab('Weekly Rental') + 
    ggtitle('Long Term Rentals') + 
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(), 
          plot.title = element_text(hjust = 0.5))

  # Nightly Rate plot
  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) + 
    geom_density(fill=str.col, alpha=.8) + 
    ylab('Frequency') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') + 
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(), 
          plot.title = element_text(hjust = 0.5))

@@

```{r ltprice_fltr2s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3.5, fig.cap='Rates and Rents by Tenure Type'}

@@

  # Make map
  loc.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
    scale_fill_manual(values=c('gray10', 'gray40', 'gray70'),
                      labels=c('Inner      ',
                               'Middle      ',
                               'Outer')) +
    geom_path(data=subs, aes(x=long, y=lat, group=group), col='gray90', size=.1, alpha=.2) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(), 
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    ggtitle("Melbourne Suburb Classifications")

@@

```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=5, fig.cap='Melbourne Suburb Classifications'}

@@

  abb.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    theme(legend.position = 'bottom',
          legend.title = element_blank(), 
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('AirBNB Location\nBy Submarket')

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
   theme(legend.position = 'bottom',
          legend.title = element_blank(), 
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long Term Rental Location\nBy Submarket')

@@

```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9}

@@

  abbtype.map <- ggplot() +
    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle('AirBNB Property Type By Submarket')

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle('Long Term Property Type By Submarket')

@@

```{r abbtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}

  abbtype.map

```{r ltrtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=9,fig.height=3.5}

  ltrtype.map
